Cell Decomposition of Rank 2 Quiver Grassmannians

### 2017-09-26 Grassmannian_cells.tex
Section 7
inserted the notion and construction of 2-quivers
section needs to be revised

\documentclass{amsart}
\usepackage{amsmath,amssymb,latexsym,color}
\usepackage[bookmarks=true,colorlinks=true, linkcolor=blue, citecolor=cyan]{hyperref}
\usepackage[margin=1in]{geometry}
\usepackage{extarrows}
\input xy
\xyoption{all}

@@

Our goal is to show that the compatible pairs provide a natural labeling for the cells of $\chi\big(Gr^Q_\bfe(P_m)\big)$ found in Theorem~\ref{???}.

>>>>

\documentclass{amsart}
\usepackage{amsmath,amssymb,latexsym,color}
\usepackage[bookmarks=true,colorlinks=true, linkcolor=blue, citecolor=cyan]{hyperref}
\usepackage{tikz}
\usepackage{pgflibraryarrows}
\usepackage{pgflibrarysnakes}
\usetikzlibrary{fit}
\usepackage[margin=1in]{geometry}
\usepackage{extarrows}
\input xy
\xyoption{all}

@@

Our goal is to show that the compatible pairs provide a natural labeling for the cells of $\chi\big(Gr^Q_\bfe(P_m)\big)$ found in Theorem~\ref{???}.
\section{Combinatorial description of non-empty cells}

\begin{definition}\begin{enumerate}
\item A $2$-quiver is a triple $Q=(Q_0,Q_1,Q_2)$ consisting of a set of vertices $Q_0$, a set of (usual) arrows $Q_1$ and a set of $2$-arrows which are arrows between full subquivers of the quiver $(Q_0,Q_1)$.

\item We call a subset $\beta\subset Q_0$ successor closed if for every arrow $v:p\to q$ we have: if $p\in \beta$, then $q\in\beta$.

\item We call a subset $\beta\subset Q_0$ strong successor closed if it is successor closed and, moreover, for every $2$-arrow $V:\Gamma(1)\to\Gamma(2)$, we have: if $\Gamma(1)_0\subset \beta$, then there exists a vertex $q\in\Gamma(2)_0$ such that $q\in\beta$.

\item Notion of equivalence of $2$-quivers to justify the transformation of $2$-arrows into usual arrows.

\end{enumerate}
\end{definition}

The aim is to associate a $2$-quiver with every preprojective representation $P_m$ and with their quotients $P_m^{(k)}$ defined in section \ref{QG}. These $2$-quivers are related to certain coefficient quivers of these representations. The upshot is that the non-empty cells of $\Gr_e(P_m)$ and $\Gr_e(P_m^{(k)})$ are in one-to-one correspondence with the strong successor closed subsets $\beta$ of type $e$. Hence the corresponding Euler characteristic can be computed when counting these subsets. It will turn out that a feature of this description is that it does not take care of the colouring of the different arrows induced by the arrows of $K(n)$.

\begin{remark}\footnote{Insert a remark that we do not work on the universal cover} 
Lemma \ref{AR} can be generalized to the cases $m\leq 2$. The only technical problem is that $\tau \tilde P^{(k)}_{m+1}$ is no quotient of $\tilde P_{m,k}$ and we have to replace it by the image of the unique morphism to $\tau \tilde P^{(k)}_{m+1}$ which induces the exact sequence.

\end{remark}

We recall the notion of Section \ref{QG} where we denote the arrows of $K(n)$ by $v_1,\ldots,v_n$. Actually, all $2$-quivers can be build from the $2$-quivers of $P_1$, $P_2$ and $P_2^{(n-1)}$ where $P_2^{(n-1)}$ depends on a choice as it is a truncated preprojective representation of dimension $(1,1)$.  Indeed, it is the cokernel of a short exact sequence
\[\ses{ P_1^{n-1}}{ P_2}{P_2^{(n-1)}}\]
for which we have $n-1$ choices. Without loss of generality, we make the following choice when defining
$$P_2^{(n-1)}=j^{(n-1)}_2\xlongleftarrow{v_1}i^{(n-1)}_2=P_1^{(1)}=j^{(1)}_1\xlongleftarrow{v_1}i^{(1)}_1$$
by its coefficient quiver. Denoting by $j_1$ the single vertex of the coefficient quiver of $P_1$, we have 
$$\Ext(P_2^{(n-1)},P_1)=\langle i^{(n-1)}_{2}\xrightarrow{v_l}j_1\mid l=2,\ldots,n\rangle.$$

This defines recursively the representation $P_{2}^{(k)}$ for $k=n-1,\ldots,0$ with $P_2^{(0)}=P_2$ when considering the short exact sequences
\[\ses{P_1}{P_2^{(k)}}{P_2^{(k+1)}}\]
by the coefficient quivers
\[\xymatrix@R10pt@C20pt{&&j^{(k)}_{2,1}\\ i^{(k)}_2\ar^{v_1}[rru]\ar^{v_{n-k}}[rrd] &&\vdots\\&&j^{(k)}_{2,n-k}}.\]
Note that we have a short exact sequence
\[\ses{\Hom(P_1,P_1)}{\Ext(P_2^{(k)},P_1)}{\Ext(P_2^{(k+1)},P_1)}\]
where a basis of $\Ext(P_2^{(k)},P_1)$ consists of the last $k$ basis elements of the basis of $\Ext(P_2^{(n-1)},P_1)$.
We define the $2$-quiver of $P_2^{(k)}$ by
\\

\begin{tikzpicture}
\tikzstyle{box} = [rectangle, minimum width=2cm, minimum height=1cm, text centered, draw=black]
\draw (0,0) node (A) {$j^{(k)}_{2,n-k}$} +(2.5,0) node (B) {$j^{(k)}_{2,n-k-1}$}+(2.5,-.8) node (P1) {\footnotesize$P_2^{(k+1)}$} +(5,0) node (B1) {$\dots$} +(7.5,0) node (C) {$j^{(k)}_{2,2}$} +(7.5,-.7) node (P3) {\footnotesize$P_2^{(n-2)}$}+(10,0) node (D) {$j^{(k)}_{2,1}$}  +(12.5,0) node (E) {$i^{(k)}_2$} +(10,-.6) node (P4) {\footnotesize$P_2^{(n-1)}$}; 
\node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
\node (Q2) [draw=black,fit={(Q1) (C) (P3)}]{};
\node (Q2b)[draw=black,fit={(Q2) (B1) }]{};

\node (Q3)[draw=black,fit={(Q2b) (B) (P1)}]{};
\draw[<-] (D)--(E) node[pos=.5,above] {$v_1$};
\draw[->,red] (Q1)--(C) node[pos=.5,above] {$v_2$};
\draw[->,red] (Q2)--(B1) node[pos=.5,above] {$v_3$};
\draw[->,red] (Q2b)--(B) node[pos=.5,above] {$v_{n-k-1}$};

\draw[->,red] (Q3)--(A) node[pos=.5,above] {$v_{n-k}$};
\end{tikzpicture}
\\

\noindent
where the $2$-arrows are coloured red. As the number of strong successor closed subsets of this $2$-quiver coincides with the number of successor closed subsets of the coefficient quiver, for clearness reasons, we will mostly work with the coefficient quiver instead.

The next step is to define the $2$-quivers of $P^{(k)}_3$ whence the remaining $2$-quivers can be obtained recursively. First we choose the basis of $\Ext(P_2^{(1)},P_2)$ given by the linear maps
$$\{i_2^{(n-1)}\xlongrightarrow{v_n}j_{2,i}\mid i=n-1,\ldots,1\}.$$
This basis gives rise to the following $2$-quiver of $P_3^{(k)}$ where we drop the indices of the vertices in abuse of notation.
\\

\begin{tikzpicture}[scale=1.4]
\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,.5) node (J12) {$\bullet$} +(1,0.1) node (D1) { $\vdots$}+(1,-.5) node (J1N1) {$\bullet$} +(1,-1) node (J1N) {$\bullet$} ; 
\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$v_1$};
\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$v_2$};
\draw[->] (I1)--(J1N1) node[pos=.7,above,sloped]{\scriptsize$v_{n-1}$};
\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};

\draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,.5) node (J22) {$\bullet$}+(1,0.1) node (D2) { $\vdots$} +(1,-.5) node (J2N1) {$\bullet$} +(1,-1) node (J2N) {$\bullet$} +(0.1,-1.3) node (P1) {\footnotesize$P_3^{(1)}$} ; 
\draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$v_1$};
\draw[->] (I2)--(J22) node[pos=.7,above,sloped]{\scriptsize$v_2$};
\draw[->] (I2)--(J2N1) node[pos=.7,above,sloped]{\scriptsize$v_{n-1}$};
\draw[->] (I2)--(J2N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};

\draw (4,0) node (DOTS) {$\dots$}+(0,-1.2) node (P2b) {\footnotesize$P_3^{(2)}$};

\draw (6,0) node (I3) {$\bullet$} +(1,1) node (J31) {$\bullet$}   +(1,.5) node (D31) { $\vdots$} +(1,-.1) node (J3N2) {$\bullet$} +(1,-.55) node (J3N1) { $\bullet$} +(1,-1) node (J3N) {$\bullet$} +(0.2,-1.1) node (P3) {\footnotesize$P_3^{(n-3)}$} ; 
\draw[->] (I3)--(J31) node[pos=.7,above,sloped]{\scriptsize$v_1$};
\draw[->] (I3)--(J3N2) node[pos=.7,above,sloped]{\scriptsize$v_{n-2}$};
\draw[->] (I3)--(J3N1) node[pos=.7,above,sloped]{\scriptsize$v_{n-1}$};
\draw[->] (I3)--(J3N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};

\draw (8,0) node (I4) {$\bullet$} +(1,1) node (J41) {$\bullet$} +(1,.5) node (J42) {$\bullet$} +(1,0) node (D4) { $\vdots$} +(1,-.5) node (J4N1) {$\bullet$} +(1,-1) node (J4N) {$\bullet$} +(0.2,-1) node (P4) {\footnotesize$P_3^{(n-2)}$}; 
\draw[->] (I4)--(J41) node[pos=.7,above,sloped]{\scriptsize$v_1$};
\draw[->] (I4)--(J42) node[pos=.7,above,sloped]{\scriptsize$v_2$};
\draw[->] (I4)--(J4N1) node[pos=.7,above,sloped]{\scriptsize$v_{n-1}$};
\draw[->] (I4)--(J4N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};

\draw (10,0) node (I5) {$\bullet$} +(1,1) node (J51) {$\bullet$} +(1,.5) node (J52) {$\bullet$} +(1,0) node (D5) { $\vdots$} +(1,-.5) node (J5N1) {$\bullet$} +(0.2,-.6) node (P5) {\footnotesize$P_3^{(n-1)}$}   ; 
\draw[->] (I5)--(J51) node[pos=.7,above,sloped]{\scriptsize $v_1$};
\draw[->] (I5)--(J52) node[pos=.7,above,sloped]{\scriptsize $v_2$};
\draw[->] (I5)--(J5N1) node[pos=.7,above,sloped]{\scriptsize $v_{n-1}$};
%\tikzstyle{every node}=[circle,fill=white!10]
\node (Q2) [draw=black,fit={(P5) (I5) (J51) (J52) (J5N1)}]{};
%\node (R2) [draw=black,fit={(I4) (J4N1)}, sloped]{};
\draw[->,red] (Q2)--(J4N1) node[pos=.5,above,sloped]{$v_{n}$};
\node (Q3) [draw=black,fit={(P4) (Q2) (I4) (J41) (J42) (J4N1) (J4N)}]{};
\draw[->,red] (Q3)--(J3N2)  node[pos=.5,above,sloped] {$v_{n}$};
\node (Q4) [draw=black,fit={(P3) (Q3) (I3) (J31) (J3N1) (J3N2) (J3N)}]{};
\draw[->,red] (Q4)--(DOTS)  node[pos=.5,above] {$v_{n}$};
\node (Q4b) [draw=black,fit={(P2b) (Q4) (DOTS)}]{};

\node (Q5) [draw=black,fit={(P1) (Q4b) (I2) (J21) (J22) (J2N1) (J2N)}]{};
\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped,sloped] {$v_{n}$};
\draw[->,red] (Q4b)--(J22)  node[pos=.5,above,sloped] {$v_{n}$};
\draw[->,red] (Q5)--(J11)  node[pos=.5,above,sloped] {$v_{n}$};

\end{tikzpicture}
\\

We have $\dim \Hom(P_m,\tau P_m^{(k)})=\dim\Ext(P_m^{(k)},P_m)=n-k$. If a basis of $\Ext(P_m^{(k)},P_m)$ is compatible with a lift to the universal covering, Lemma \ref{AR} gives a one-to-one correspondence between basis elements of $\Ext(P_m^{(k)},P_m)$ and $\Hom(P_{m-1},\tau P_m^{(k)})$. Let us consider the case $m=3$. The coefficient quiver of $\tau P_3^{(k)}$ is given by
\[\xymatrix@R10pt@C20pt{&&i_{1}\ar_{v_1}[lld]\\ j &&\vdots\\&&i_{k}\ar_{v_{k}}[llu]}.\]
The image of the homomorphism of the corresponding exact sequence induced by the basis element $i_2^{(n-1)}\xrightarrow{v_n} j_{2,l}$ is the quotient quiver $j\xlongleftarrow{v_l} i_l$. Thus in this case the $2$-arrow connects the $2$-quiver of $P_3^{(k)}$ to the image of the corresponding homomorphism $P_2\to P_1^{(k)}$ which is of dimension $(1,1)$. In the above illustration, we forgo to insert the corresponding rectangles and just connected the $2$-arrows to the sinks of the corresponding subquivers. It can be seen that this is no restriction from the combinatorial point of view.

Now we can recursively the $2$-quivers of $P_m^{(k)}$ for $m\geq 4$ and $k=n-1,\ldots,0$ when repeating this procedure. For $m\geq 4$, the truncated preprojective $\tau P_m^{(k)}$ can uniquely be found as a quotient of $P_m$.
Recall that we have $\udim P_m^{(k)}=\udim P_{m-1}^{(1)}+(n-k-1)\udim P_{m-1}$. Moreover, we have 
\[\dim \Hom(P_{m-1},\tau P_m^{(1)})=\dim\Ext(P_m^{(1)},P_{m-1})=n-1.\]

As before we get a one-to-one correspondence between basis elements when passing to the universal covering quiver. More precisely, we can take the BGP-reflected basis of the basis of $\Ext(P_2^{(1)},P_2)$ from above.

Let us assume that we already constructed the $2$-quiver of $P_{m+1}^{(k)}$. The $2$-quiver of $P^{(k-1)}_{m+1}$ is given by glueing the $2$-quiver of $P_{m+1}^{(k)}$ to the one of $P_{m}$
\\

\begin{tikzpicture}
\draw (0,4) node (A1) {$P_{m-1}$}+(0,-1.2) node (PM) {\footnotesize$P_{m}$} +(1.5,0) node (B1) {$P_{m-1}$}+(1.5,-1.1) node (P11) {\footnotesize$P_{m}^{(1)}$} +(3,0) node (B11) {$\dots$} +(4.5,0) node (D1) {$P_{m-1}$}  +(6,0) node (E1) {$P_{m-2}$} +(4.5,-1) node (P41) {\footnotesize$P_{m}^{(n-2)}$}+(6,-.9) node (P51) {\footnotesize$P_{m-1}^{(1)}$}+(7.5,0) node (A1b) {$\dots$} +(9,0) node (B1b) {$P_{m-2}$}+(9,-.8) node (P11b) {\footnotesize$P_{m-1}^{(k)}$} +(10.5,0) node (B11b) {$\dots$} +(12,0) node (D1b) {$P_{m-2}$} +(12,-.6) node (P41b) {\footnotesize$P_{m-1}^{(n-2)}$} +(13.5,0) node (E1b) {$P^{(n-1)}_{m-2}$} ; 
\node (Q11) [draw=black,fit={(D1b) (E1b) (P41b)}]{};
\node (Q21) [draw=black,fit={(Q11) (B11b)}]{};
\node (Q31)[draw=black,fit={(Q21) (B1b) (P11b)}]{};
\node (Q41)[draw=black,fit={(Q31) (A1b)}]{};
\node (Q51)[draw=black,fit={(Q41) (E1)}]{};
\node (Q61)[draw=black,fit={(Q51) (P41) (D1)}]{};
\node (Q71)[draw=black,fit={(Q61) (B11)}]{};
\node (Q81)[draw=black,fit={(Q71) (P11) (B1)}]{};
\node (Q91)[draw=black,fit={(Q81) (A1)}]{};
\draw[<-,red] (D1b)--(E1b) node[pos=.5,above] {};
\draw[->,red] (Q11)--(B11b) node[pos=.5,above] {$$};
\draw[->,red] (Q21)--(B1b) node[pos=.5,above] {$$};
\draw[->,red] (Q31)--(A1b) node[pos=.5,above] {$$};
\draw[->,red] (Q41)--(E1) node[pos=.5,above] {$$};
\draw[->,red] (Q51)--(D1) node[pos=.5,above] {$$};
\draw[->,red] (Q61)--(B11) node[pos=.5,above] {$$};
\draw[->,red] (Q71)--(B1) node[pos=.5,above] {$$};
\draw[->,red] (Q81)--(A1) node[pos=.5,above] {$$};

\draw (0,0) node (B) {$P_{m}$}+(0,-.8) node (P1) {\footnotesize$P_{m+1}^{(k)}$} +(2.5,0) node (B1) {$\dots$} +(5,0) node (C) {$P_{m}$} +(5,-.7) node (P3) {\footnotesize$P_{m+1}^{(n-2)}$}+(7.5,0) node (D) {$P_{m}$}  +(10,0) node (E) {$P_{m+1}^{(n-1)}=P_{m}^{(1)}$} +(7.5,-.6) node (P4) {\footnotesize$P_{m+1}^{(n-1)}$}; 
\node (Q1) [draw=black,fit={(D) (E) (P4)}]{};
\node (Q2) [draw=black,fit={(Q1) (C) (P3)}]{};
\node (Q2b)[draw=black,fit={(Q2) (B1) }]{};

\draw[<-,red] (D)--(E) node[pos=.5,above] {};
\draw[->,red] (Q1)--(C) node[pos=.5,above] {$$};
\draw[->,red] (Q2)--(B1) node[pos=.5,above] {$$};
\draw[->,red] (Q2b)--(B) node[pos=.5,above] {$$};

\node (PMK) [draw=black, thick,fit={(Q2b) (B)}]{};
\draw[->,red,thick] (PMK)--(Q31);
\end{tikzpicture}
\\

\noindent where the $2$-arrows connects the $2$-quiver of $P_{m+1}^{(k)}$ to its Auslander-Reiten translate $\tau P_{m+1}^{(k)}= P_{m-1}^{(k)}$ in $P_m$. This subquiver can be found at the very right of the $2$-quiver of $P_m$. Note that forgo the colouring of the arrows as it does not play any role from the combinatorial point of view. For $n=3$ the $2$-quiver of $P_3$ is given by:\\

\begin{tikzpicture}[scale=1]
\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$a$};
\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$b$};
\draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};

\draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,0) node (J22) {$\bullet$} +(1,-1) node (J23) {$\bullet$}; 
\draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$a$};
\draw[->] (I2)--(J22) node[pos=.7,above,sloped]{\scriptsize$b$};
\draw[->] (I2)--(J23) node[pos=.7,above,sloped]{\scriptsize$c$};
%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
\draw (6,0) node (I3) {$\bullet$} (5,0) node (J31) {$\bullet$} (4,0) node (J33) {$\bullet$}; 
\draw[->] (I3)--(J31) node[pos=.5,above,sloped]{\scriptsize$a$};
%\draw[->] (I3)--(J32) node[pos=.7,above,sloped]{\scriptsize$b$};
%\draw[->] (I3)--(J33) node[pos=.7,above,sloped]{\scriptsize$c$};
%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
\node (Q0)[draw=black,fit={(I3) (J31) }]{};
\node (Q1)[draw=black,fit={(Q0) (J33)}]{};
\node (Q2)[draw=black,fit={(Q1) (I2) (J21) (J22) (J23)}]{};

%\node (Q3)[draw=black,fit={(Q2b) (B) (P1)}]{};
\draw[->,red] (Q0)--(J33) node[pos=.5,above] {\scriptsize $b$};
\draw[->,red] (Q1)--(J22) node[pos=.5,above] {\scriptsize $c$};
\draw[->,red] (Q2)--(J11) node[pos=.5,above] {\scriptsize $c$};
\end{tikzpicture}
\\

The one of $P_4$ is given by:\\

\begin{tikzpicture}[scale=1]
\draw (0,0) node (I1) {$\bullet$} +(1,1) node (J11) {$\bullet$} +(1,0) node (J12) {$\bullet$} +(1,-1) node (J13) {$\bullet$}; 
\draw[->] (I1)--(J11) node[pos=.7,above,sloped]{\scriptsize$a$};
\draw[->] (I1)--(J12) node[pos=.7,above,sloped]{\scriptsize$b$};
\draw[->] (I1)--(J13) node[pos=.7,above,sloped]{\scriptsize$c$};
%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};

\draw (2,0) node (I2) {$\bullet$} +(1,1) node (J21) {$\bullet$} +(1,0) node (J22) {$\bullet$} +(1,-1) node (J23) {$\bullet$}; 
\draw[->] (I2)--(J21) node[pos=.7,above,sloped]{\scriptsize$a$};
\draw[->] (I2)--(J22) node[pos=.7,above,sloped]{\scriptsize$b$};
\draw[->] (I2)--(J23) node[pos=.7,above,sloped]{\scriptsize$c$};
%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
\draw (6,0) node (I3) {$\bullet$} (5,0) node (J31) {$\bullet$} (4,0) node (J33) {$\bullet$}; 
\draw[->] (I3)--(J31) node[pos=.5,above,sloped]{\scriptsize$a$};
%\draw[->] (I3)--(J32) node[pos=.7,above,sloped]{\scriptsize$b$};
%\draw[->] (I3)--(J33) node[pos=.7,above,sloped]{\scriptsize$c$};
%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};
\node (Q0)[draw=black,fit={(I3) (J31) }]{};
\node (Q1)[draw=black,fit={(Q0) (J33)}]{};
\node (Q2)[draw=black,fit={(Q1) (I2) (J21) (J22) (J23)}]{};

%\node (Q3)[draw=black,fit={(Q2b) (B) (P1)}]{};
\draw[->,red] (Q0)--(J33) node[pos=.5,above] {\scriptsize $b$};
\draw[->,red] (Q1)--(J22) node[pos=.5,above] {\scriptsize $c$};
\draw[->,red] (Q2)--(J11) node[pos=.5,above] {\scriptsize $c$};

\draw (0,-4) node (I1b) {$\bullet$} +(1,1) node (J11b) {$\bullet$} +(1,0) node (J12b) {$\bullet$} +(1,-1) node (J13b) {$\bullet$}; 
\draw[->] (I1b)--(J11b) node[pos=.7,above,sloped]{\scriptsize$a$};
\draw[->] (I1b)--(J12b) node[pos=.7,above,sloped]{\scriptsize$b$};
\draw[->] (I1b)--(J13b) node[pos=.7,above,sloped]{\scriptsize$c$};
%\draw[->] (I1)--(J1N) node[pos=.7,above,sloped]{\scriptsize$v_{n}$};

\draw (2,-4) node (I2b) {$\bullet$} +(1,1) node (J21b) {$\bullet$} +(1,0) node (J22b) {$\bullet$} +(1,-1) node (J23b) {$\bullet$}; 
\draw[->] (I2b)--(J21b) node[pos=.7,above,sloped]{\scriptsize$a$};
\draw[->] (I2b)--(J22b) node[pos=.7,above,sloped]{\scriptsize$b$};
\draw[->] (I2b)--(J23b) node[pos=.7,above,sloped]{\scriptsize$c$};

\draw (6,-4) node (I3b) {$\bullet$} (5,-4) node (J31b) {$\bullet$} (4,-4) node (J33b) {$\bullet$}; 
\draw[->] (I3b)--(J31b) node[pos=.5,above,sloped]{\scriptsize$a$};
\node (Q0b)[draw=black,fit={(I3b) (J31b) }]{};
\node (Q1b)[draw=black,fit={(Q0b) (J33b)}]{};
\node (Q2b)[draw=black,fit={(Q1b) (I2b) (J21b) (J22b) (J23b)}]{};

\draw[->,red] (Q0b)--(J33b) node[pos=.5,above] {\scriptsize $b$};
\draw[->,red] (Q1b)--(J22b) node[pos=.5,above] {\scriptsize $c$};
\draw[->,red] (Q2b)--(J11b) node[pos=.5,above] {\scriptsize $c$};

\draw (9,-4) node (I2c) {$\bullet$} +(1,1) node (J21c) {$\bullet$} +(1,0) node (J22c) {$\bullet$} +(1,-1) node (J23c) {$\bullet$}; 
\draw[->] (I2c)--(J21c) node[pos=.7,above,sloped]{\scriptsize$a$};
\draw[->] (I2c)--(J22c) node[pos=.7,above,sloped]{\scriptsize$b$};
\draw[->] (I2c)--(J23c) node[pos=.7,above,sloped]{\scriptsize$c$};

\draw (13,-4) node (I3c) {$\bullet$} (12,-4) node (J31c) {$\bullet$} (11,-4) node (J33c) {$\bullet$}; 
\draw[->] (I3c)--(J31c) node[pos=.5,above,sloped]{\scriptsize$a$};
\node (Q0c)[draw=black,fit={(I3c) (J31c) }]{};
\node (Q1c)[draw=black,fit={(Q0c) (J33c)}]{};
\node (Q2c)[draw=black,fit={(Q1c) (I2c) (J21c) (J22c) (J23c)}]{};
\node (Q3c)[draw=black,fit={(Q2c) (Q2b) (I1b)}]{};
\draw[->,red] (Q0c)--(J33c) node[pos=.5,above] {\scriptsize $b$};
\draw[->,red] (Q1c)--(J22c) node[pos=.5,above] {\scriptsize $c$};
\draw[->,red] (Q2c)--(Q0b) node[pos=.5,above] {\scriptsize $b$};
\draw[->,red] (Q3c)--(Q1) node[pos=.6,above] {\scriptsize $c$};

\end{tikzpicture}

\begin{theorem}
The Euler characteristic $\chi(\Gr_e(P_m^{(k)}))$ is given by the number of strong successor closed subsets of type $e$ of the $2$-quiver of $P_m^{(k)}$.
\end{theorem}
